Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-26 paper.qmd
improved fig 5

::: {#fig-user-stories}
![](images/mermaid-figure-1.png)

>>>>

```{r alternative}
# https://www.sesync.org/resources/creating-visualizations-diagrammer
schematic = DiagrammeR::grViz("
digraph {
  # graph statement
  #################
  graph [rankdir = LR
         color = white
         fontsize = 36]

  # nodes (rectangles)
  #################
   node [shape = rectangle            
       margin = 0.4
       fontsize = 36
       fixedsize = false
       width = 1]

   subgraph cluster_2 {
     graph[shape = rectangle]
         C2b [label = 'Exploration']
         C2a [label = 'CRUSE\ncounty level results']
         C2 [label = 'CRUSE\nnational map']
         B2 [label = 'CRUSE\nlanding page']
         A2 [label = 'Non professional\nuser'] 
}

   subgraph cluster_1 {
   graph[shape = rectangle]
         Dd [label = 'Data dowloads']
         Dc [label = 'Quiet and fast route\nnetworks']
         Db [label = 'County statistics']
         Da [label = 'Full county map']
         D [label = 'CRUSE\ncounty map']
         C [label = 'CRUSE\nnational map']
         B [label = 'CRUSE\nlanding page']
         A [label = 'Professional user'] 
}

  # node (triangle)
  #################
  node [shape = diamond]
         Dd1 [label = 'External\ntools']
         C2b1 [label = 'Communication']
  # edges 
  #######
  A2 -> B2
  A -> B
  B -> C
  B2 -> C2
  C -> D
  C2 -> C2a
  C2 -> C2b
  C2b -> C2b1
  D -> Da 
  D -> Db 
  D -> Dc 
  D -> Dd 
  Dd -> Dd1

}
")
# schematic
# htmlwidgets::saveWidget(schematic, "images/fig5.html")
# browseURL("images/fig5.html")
# webshot2::webshot(url = "images/fig5.html", file = "images/fig5.png")
knitr::include_graphics("images/fig5.png")
```

::: {#fig-user-stories}
![](images/fig5.png)
